DRAFT: Harmonized and trait aggregation paper

### 2020-11-25 Paper/Draft_harmonization_paper.tex
25.11: Small changes before send to Ralf

The definition of grouping features varied across databases mainly concerning their differentiation into traits but also in their scope. We provide a summary of discrepancies in trait definitions in the appendix (Table S\ref{stab:trait_definitions}). Both, differences in differentiation and scope can lead to discrepancies in trait definitions. For example, for the grouping feature feeding mode discrepancies arise because traits are assigned in different ways. The Tachet database defines predators as carvers, engulfers and swallowers. By contrast, in the North American (Twardochleb et al.) database predators are defined as engulfers and carnivorous piercers. In turn, in the Tachet database, piercers are defined as a separate trait encompassing herbivorous and carnivorous piercers. Furthermore, the scope in the freshwaterecology.info database for feeding mode is primarily on the food source of a species (except for filterers), while the other databases focus on the strategies of food acquisition. Therefore, the freshwaterecology.info database defines e.g. predator as "eating from prey", while the other databases use the mouthpart morphology as basis of their definition. The Tachet database captures the food source in an additional grouping feature. Varying levels of differentiation are also present in all other investigated grouping features between the trait databases (Table \ref{tab:trait_databases_coding_differentiation} and Table S\ref{stab:trait_definitions}). Locomotion definitions differ also in scope between databases. Freshwaterecology.info and New Zealand databases describe locomotion as the way of movement of an organism, Tachet as substrate relation and locomotion, the North American (Vieira et al.) as how organisms deal with flow, Australia as attachment, and the North American (Twardochleb et al.) database includes not only the way of movement, but also the location of movement. Similarly, regarding the reproduction traits, databases differ in their scope. Reproduction is captured in one grouping feature and defined as location of oviposit clutches and mode of reproduction in the freshwaterecology.info and Tachet databases. North America (Vieira et al.) provides information on the oviposition location but not on reproductive behavior. The Australian database report traits for reproductive behavior but also on oviposition site. The New Zealand database distinguishes three grouping features related to reproduction: reproductive technique, oviposition site (e.g. water surface, terrestrial), and egg/egg mass (e.g. free, cemented).

@@

Comparing the aggregated trait affinities, in total 15000 ($500$ aggregated traits $*10$ unique comparisons of trait affinities and $3$ scenarios), for each simulated dataset showed that in most simulated datasets the differences between the aggregated traits were small. Only 1.42 \% (213 out of 15.000) of all comparisons showed a difference equal or greater than an absolute trait affinity of 0.1. Most of these differences occurred for the \textit{sim\_extreme} scenario (83.5 \%). The majority of the differences equal or above 0.1 were found between the aggregation methods \textit{direct\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}, and \textit{stepwise\_agg\textsubscript{median}} and \textit{weighted\_agg} (Figure S\ref{fig:sim_indv_runs}). 
% Differences were rather small, largest difference 0.265 for sim_extreme (stepwise_median vs weighted_agg)

@@

% Is that necessary?
A comparison of the aggregation methods with each other for the 4 datasets revealed that differences in aggregated trait affinities were largest between the \textit{stepwise\_agg\textsubscript{median}} and \textit{direct\_agg\textsubscript{median}} (Figure S\ref{fig:comp_aggr_methods}).

@@

% Discussion/Comparison aggr. methods/assigned traits  
Our results show that aggregation of traits by the median compared to aggregating by the mean is often closer to the assigned traits at family level. However, in those cases where differences between trait aggregation methods that use the median and assigned traits occurred, these differences were greater compared to the aggregation methods that used the mean. The different weighting methods, i.e. aggregating stepwise, direct or weighted, did not seem to have a strong impact, because the distribution of absolute trait affinity differences to assigned traits obtained by the \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}} and \textit{weighted\_agg} were relatively similar in both tested datasets. This also applies to the distributions of absolute trait affinity differences obtained by \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}. Instead, using the mean or the median changed the distribution of differences in trait affinities between aggregated and assigned traits. A possible reason why the use of different weightings for taxa had little impact on trait aggregation is that a considerable portion of taxa used have a low numbers of genera or species entries. From the taxa that were compared from the North American trait dataset to the assigned traits at family-level, 13.8 \% were resolved on family-level and 61.7 \% were resolved on genus-level. 52.1 \% had 5 or less genera and 12.8 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}). In the Australian dataset 21.4 \% of the compared taxa had trait information resolved on family-level, 39.5 \% resolved on genus level, and 39.1 \% resolved on species-level. 67.73 \% of the taxa contain 5 or less genera and 39.6 \% just contained one genus (Figure \ref{fig:tax_hierarchy_AUS}). The simulation results indicated that the choice of the aggregation method for small numbers of genera per family (5) can be important when one genus has a much larger number of species compared to other genera within a particular family. % How often in the trait datasets?

% Differences between Results of AUS and NOA dataset
Observed differences between aggregated and assigned traits were higher for the North American trait dataset. This can be explained by the binary coding of the traits in the North American dataset. As a results, traits have been assigned affinities of either 1 or 0.  Therefore, traits of a certain grouping feature have in most cases a higher difference in trait affinities to each other than if they were coded with fuzzy codes.

% Discussion on differences between aggregated and assigned traits  
Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular family is. Aggregation of trait information on species or genus-level to a point estimate on family-level suggests a precision which is not necessarily present, especially not for traits with a high variability or if trait information on species-level is missing. In fact, traits can vary strongly on more precise taxonomic levels than the family-level. For example, Monaghan and Soares found a high intra-family trait dispersion in the Tachet database for traits of the grouping features body size, flow preference, and reproduction \cite{monaghan_improving_2013}. Furthermore, studies focusing on the lability of traits, i.e. how much traits are unconstrained by phylogeny, found that traits of ecological preferences (e.g. thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable \cite{poff_functional_2006, wilkes_traitbased_2020}. Our analysis showed that disagreement between aggregated and assigned traits was largest for body size and respiration traits. The highest possible difference of 1 between aggregated trait affinities and assigned trait affinities (in total in 6.9 \% of all cases) for the Australian dataset occurred most often for body size large and medium (42.5 \% and 39.2 \% of all cases with a difference of 1, respectively) across all comparisons of aggregated and assigned traits. Both traits had also the highest mean and standard deviation in the absolute difference of trait affinities across all comparisons (size medium: mean 0.5, sd 0.29; size large: mean 0.59, sd 0.32). A reason for this is also that body size was coded binary. For the taxa compared from the North American dataset, the highest possible difference in trait affinities occurred most often for the trait body size medium (15.8 \% of all cases with the maximum difference of 1), followed by the traits respiration via plastron and spiracle and respiration via tegument (both 13 \% of all cases with a maximum difference of 1). Respiration via plastron and spiracle showed the highest mean and standard deviation of the absolute difference of trait affinities across all comparisons (mean 0.71, sd 0.33), followed by respiration via tegument (mean 0.5, sd 0.34) and body size medium (mean 0.49, sd 0.3).

% Our attempt to synthesize trait information showed

% Conclude:
% The uncertainty of trait information should be taken into account when aggregating traits is necessary and appropriate measures to capture this uncertainty should be established. 
% ? What measures could this be, e.g. report SD

% Include which traits are more consistent?
% How have the aggregation and assignments performed when looking back at the original data?

% Include?:
% What do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? Where does the classification come from?
%   - Where does the classification come from?
%     Few sources used in NOA also used in AUS:
%     AUS: Merrit & Cummins 1978/1984 for feeding mode for a few genera and families 
%     NOA: Merritt, Richard W., Cummins, Berg 2008 -> but not clear if for feeding mode as well; according to trait description "Cummins, K. W. Trophic Relations of Aquatic Insects" was used for feeding mode
%   - Could not include all data due to data gaps -> much needed to be filled -> would maybe change the picture?
% Are the differences between continents because of evolution or only because scientists have done more research in one of the continents?

@@

The re-analysis showed that neither using harmonised grouping features nor aggregated traits changed drastically the results of the original study. The traits that did not respond to the salinity gradient (i.e. not on the extremes of the conductivity axis) in the re-analysis were those closest to the criterion that defined when a trait was associated with either high or low salinity (mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see methods), namely feeding mode shredder, respiration gills, and life cycle duration traits. During harmonisation the trait shredder has been amalgamated based on three traits (Miner, xylophagus, and shredder). As a result, the trait affinities in the original dataset have a higher mean and standard deviation than in the aggregated and harmonized datasets (Table S\ref{tab:SI_resp_traits_summary_stats}). Hence, the signal in the original data for the trait shredder has presumably been weakened by the harmonization, which might be the reason that shredders showed a less strong reaction to the salinity gradient.

% Resp gil complicated: Original data has a lot of zeros, not in the harmonized & aggregated datasets
% Aggregated data look similar to the harmonized ones, but resp_gil is here one of the traits 
% responding to conductivity, while it is not when using harmonized trait data

% Why did some aggregation methods promote life cycle duration and others not?
% Mean, median and SD of these traits are all relatively similar across the aggregated datasets

>>>>

The definition of grouping features varied across databases mainly concerning their differentiation into traits but also in their scope. We provide a summary of discrepancies in trait definitions in the appendix (Table \ref{stab:trait_definitions}). Both, differences in differentiation and scope can lead to discrepancies in trait definitions. For example, for the grouping feature feeding mode discrepancies arise because traits are assigned in different ways. The Tachet database defines predators as carvers, engulfers and swallowers. By contrast, in the North American (Twardochleb et al.) database predators are defined as engulfers and carnivorous piercers. In turn, in the Tachet database, piercers are defined as a separate trait encompassing herbivorous and carnivorous piercers. Furthermore, the scope in the freshwaterecology.info database for feeding mode is primarily on the food source of a species (except for filterers), while the other databases focus on the strategies of food acquisition. Therefore, the freshwaterecology.info database defines e.g. predator as "eating from prey", while the other databases use the mouthpart morphology as basis of their definition. The Tachet database captures the food source in an additional grouping feature. Varying levels of differentiation are also present in all other investigated grouping features between the trait databases (Table \ref{tab:trait_databases_coding_differentiation} and Table \ref{stab:trait_definitions}). Locomotion definitions differ also in scope between databases. Freshwaterecology.info and New Zealand databases describe locomotion as the way of movement of an organism, Tachet as substrate relation and locomotion, the North American (Vieira et al.) as how organisms deal with flow, Australia as attachment, and the North American (Twardochleb et al.) database includes not only the way of movement, but also the location of movement. Similarly, regarding the reproduction traits, databases differ in their scope. Reproduction is captured in one grouping feature and defined as location of oviposit clutches and mode of reproduction in the freshwaterecology.info and Tachet databases. North America (Vieira et al.) provides information on the oviposition location but not on reproductive behavior. The Australian database report traits for reproductive behavior but also on oviposition site. The New Zealand database distinguishes three grouping features related to reproduction: reproductive technique, oviposition site (e.g. water surface, terrestrial), and egg/egg mass (e.g. free, cemented).

@@

Comparing the aggregated trait affinities, in total 15000 ($500$ aggregated traits $*10$ unique comparisons of trait affinities and $3$ scenarios) for each simulated dataset showed that in most simulated datasets the differences between the aggregated traits were small. Only 1.42 \% (213 out of 15.000) of all comparisons showed a difference equal or greater than an absolute trait affinity of 0.1. Most of these differences occurred for the \textit{sim\_extreme} scenario (83.5 \%). The majority of the differences equal or above 0.1 were found between the aggregation methods \textit{direct\_agg\textsubscript{mean}} and \textit{stepwise\_agg\textsubscript{median}}, \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}, and \textit{stepwise\_agg\textsubscript{median}} and \textit{weighted\_agg} (Figure \ref{fig:sim_indv_runs}). 
% Differences were rather small, largest difference 0.265 for sim_extreme (stepwise_median vs weighted_agg)

@@

% Is that necessary?
A comparison of the aggregation methods with each other for the 4 datasets revealed that differences in aggregated trait affinities were largest between the \textit{stepwise\_agg\textsubscript{median}} and \textit{direct\_agg\textsubscript{median}} (Figure \ref{fig:comp_aggr_methods}).

@@

Our results indicated that aggregation of traits by the median compared to aggregating by the mean is often closer to the assigned traits at family level. However, in those cases where differences between trait aggregation methods that use the median and assigned traits occurred, these differences were greater compared to the aggregation methods that used the mean. The different weightings used by the aggregation methods, i.e. aggregating stepwise, direct or weighted, did not seem to have a strong impact, because the distribution of absolute trait affinity differences to assigned traits obtained by the \textit{direct\_agg\textsubscript{mean}}, \textit{stepwise\_agg\textsubscript{mean}} and \textit{weighted\_agg} were relatively similar in both tested datasets. This also applies to the distributions of absolute trait affinity differences obtained by \textit{direct\_agg\textsubscript{median}} and \textit{stepwise\_agg\textsubscript{median}}. Instead, using the mean or the median changed the distribution of differences in trait affinities between aggregated and assigned traits. A possible reason why the use of different weightings for taxa had little impact on trait aggregation is that a considerable portion of taxa used have low numbers of genera or species entries. From the taxa that were compared from the North American trait dataset to the assigned traits at family-level, 13.8 \% were resolved on family-level and 61.7 \% were resolved on genus-level. 52.1 \% had 5 or less genera and 12.8 \% contained just one genus (Figure \ref{fig:tax_hierarchy_NOA}). In the Australian dataset 21.4 \% of the compared taxa had trait information resolved on family-level, 39.5 \% resolved on genus level, and 39.1 \% resolved on species-level. 67.73 \% of the taxa contain 5 or less genera and 39.6 \% just contained one genus (Figure \ref{fig:tax_hierarchy_AUS}). The simulation results indicated that the choice of the aggregation method for small numbers of genera per family (5) can be important when one genus has a much larger number of species compared to other genera within a particular family. % How often in the trait datasets?

% Improve wording
Observed differences between aggregated and assigned traits were higher for the North American trait dataset. This can be explained by the binary coding of the traits in the North American dataset. As a result, traits have been assigned affinities of either 1 or 0.  Therefore, traits of a certain grouping feature have in most cases a higher difference in trait affinities to each other than if they were coded with fuzzy codes.

% Discussion on differences between aggregated and assigned traits  
Evaluation of the differences between aggregated and assigned traits is difficult because it remains unclear what the true value of a particular trait for a particular family is. Aggregation of trait information on species or genus-level to a point estimate on family-level suggests a precision which is not necessarily present, especially not for traits with a high variability or if trait information on species-level is missing. Some traits can vary strongly on more precise taxonomic levels than the family-level. For example, Monaghan and Soares found a high intra-family trait dispersion in the Tachet database for traits of the grouping features body size, flow preference, and reproduction \cite{monaghan_improving_2013}. Furthermore, studies focusing on the lability of traits, i.e. how much traits are unconstrained by phylogeny, found that traits of ecological preferences (e.g. thermal preference), body size, resistance forms, and to a lesser extent feeding mode are labile, and thus possibly highly variable \cite{poff_functional_2006, wilkes_traitbased_2020}.
% ?Mention intra-species variation of some traits (voltinism varies along climatic gradients)
% ? Mention: obtaining trait information on species-level is challenging
% Could lead to data gaps in the datasets
% ?Would like to connect both parts, but maybe this doesn't make too much sense
Our analysis showed that disagreement between aggregated and assigned traits was largest for body size and respiration traits. The highest possible difference of 1 between aggregated trait affinities and assigned trait affinities (in total in 6.9 \% of all cases) for the Australian dataset occurred most often for body size large and medium (42.5 \% and 39.2 \% of all cases with a difference of 1, respectively) across all comparisons of aggregated and assigned traits. Both traits had also the highest mean and standard deviation in the absolute difference of trait affinities across all comparisons (size medium: mean 0.5, sd 0.29; size large: mean 0.59, sd 0.32). % A reason for this is also that body size was coded binary.
For the taxa compared from the North American dataset, the highest possible difference in trait affinities occurred most often for the trait body size medium (15.8 \% of all cases with the maximum difference of 1), followed by the traits respiration via plastron and spiracle and respiration via tegument (both 13 \% of all cases with a maximum difference of 1). Respiration via plastron and spiracle showed the highest mean and standard deviation of the absolute difference of trait affinities across all comparisons (mean 0.71, sd 0.33), followed by respiration via tegument (mean 0.5, sd 0.34) and body size medium (mean 0.49, sd 0.3). % So these traits might be highly variable, confirming the earlier mentioned studies partially.

% Conclude:
% The uncertainty of trait information should be taken into account when aggregating traits is necessary and appropriate measures to capture this uncertainty should be established. 
% Fuzzy coding is one option to express uncertainty but is not only used for variabality in traits within taxononomic groups above species-level. Also, for variation in traits during development of an organism,
% ? 
% ? Other measures possible, e.g. report SD

% Include?:
% Which traits are more consistent
% How have the aggregation and assignments performed when looking back at the original data?
% What do we really know because someone has watched the animals and published their behaviour; what is extrapolated knowledge? Where does the classification come from?
%   - Where does the classification come from?
%     Few sources used in NOA also used in AUS:
%     AUS: Merrit & Cummins 1978/1984 for feeding mode for a few genera and families 
%     NOA: Merritt, Richard W., Cummins, Berg 2008 -> but not clear if for feeding mode as well; according to trait description "Cummins, K. W. Trophic Relations of Aquatic Insects" was used for feeding mode
%   - Could not include all data due to data gaps -> much needed to be filled -> would maybe change the picture?
% Are the differences between continents because of evolution or only because scientists have done more research in one of the continents?

@@

The re-analysis showed that neither using harmonised grouping features nor aggregated traits changed drastically the results of the original study. The traits that did not respond t<o the salinity gradient (i.e. not on the extremes of the conductivity axis) in the re-analysis were those closest to the criterion that defined when a trait was associated with either high or low salinity (mahalanobis distance greater than the 97.5 \% quantile of the Chi-square distribution, see methods), namely feeding mode shredder, respiration gills, and life cycle duration traits. During harmonisation the trait shredder has been amalgamated based on three traits (Miner, xylophagus, and shredder). As a result, the trait affinities in the original dataset have a higher mean and standard deviation than in the aggregated and harmonized datasets (Table S\ref{tab:SI_resp_traits_summary_stats}). Hence, the signal in the original data for the trait shredder has presumably been weakened by the harmonization, which might be the reason that shredders showed a less strong reaction to the salinity gradient.

% Situation with Resp gil complicated: 
% - Original data has a lot of zeros, which are not anymore present in the harmonized & aggregated datasets (see Table S2)
% - In the analysis with the harmonized dataset resp_gil is not responding to the salinity gradient 
% - Aggregated data look similar to the harmonized ones, but resp_gil is here one of the traits 
% responding to conductivity!

% Why did some aggregated datasets promote life cycle duration traits and others not?
% - Results using trait data obtained when aggregating with stepwise_agg (median) and stepwise_agg (mean) indicate that life cycle duration traits are not characterising upstream or downstream sites. 
% Results using trait data obtained with the other aggregation methods indicate that life cycle duration traits characterise upstream or downstream sites.
% However: Mean, median and SD of these traits are all relatively similar across all aggregated datasets.

### 2020-11-25 Paper/Results/SI.tex
25.11: Small changes before send to Ralf

\begin{table}[ht]
    \centering
    \caption{Mean, median and standard deviation of the traits that were responsive to the salinity gradient in the original study but not when re-analysis with the harmonized dataset trait dataset.} 
    \label{tab:SI_resp_traits_summary_stats}
    \begin{tabular}{llccc}
    \toprule[.1em]
    Dataset & Trait & Mean & Median & SD \\ 
    \toprule[.1em]
    Stepw\_median & Shredder & 0.20 & 0.14 & 0.25 \\ 
      Stepw\_mean & Shredder & 0.18 & 0.12 & 0.22 \\ 
      Direct\_median & Shredder & 0.21 & 0.14 & 0.25 \\ 
      Direct\_mean & Shredder & 0.19 & 0.14 & 0.22 \\ 
      Weighted & Shredder & 0.19 & 0.14 & 0.22 \\ 
      Harmonized; not\_aggregated & Shredder & 0.18 & 0.12 & 0.24 \\ 
      Original & Shredder & 0.25 & 0.14 & 0.32 \\ 
      Stepw\_median & Gills & 0.30 & 0.27 & 0.32 \\ 
      Stepw\_mean & Gills & 0.29 & 0.22 & 0.32 \\ 
      Direct\_median & Gills & 0.30 & 0.30 & 0.32 \\ 
      Direct\_mean & Gills & 0.30 & 0.30 & 0.32 \\ 
      Weighted & Gills & 0.30 & 0.30 & 0.32 \\ 
      Harmonized; not\_aggregated & Gills & 0.30 & 0.25 & 0.32 \\ 
      Original & Gills & 0.28 & 0.00 & 0.33 \\ 
      Stepw\_median & Short life cycle & 0.64 & 0.75 & 0.39 \\ 
      Stepw\_mean & Short life cycle & 0.64 & 0.79 & 0.39 \\ 
      Direct\_median & Short life cycle & 0.67 & 0.75 & 0.37 \\ 
      Direct\_mean & Short life cycle & 0.67 & 0.79 & 0.38 \\ 
      Weighted & Short life cycle & 0.67 & 0.79 & 0.38 \\ 
      Harmonized; not\_aggregated & Short life cycle & 0.64 & 0.75 & 0.40 \\ 
      Original & Short life cycle & 0.64 & 0.75 & 0.40 \\ 
      Stepw\_median & Long life cylce & 0.36 & 0.25 & 0.39 \\ 
      Stepw\_mean & Long life cylce & 0.36 & 0.21 & 0.39 \\ 
      Direct\_median & Long life cylce & 0.33 & 0.25 & 0.37 \\ 
      Direct\_mean & Long life cylce & 0.33 & 0.21 & 0.38 \\ 
      Weighted & Long life cylce & 0.33 & 0.21 & 0.38 \\ 
      Harmonized; not\_aggregated & Long life cylce & 0.36 & 0.25 & 0.40 \\ 
      Original & Long life cylce & 0.36 & 0.25 & 0.40 \\ 
    \bottomrule
    \end{tabular}
\end{table}

@@

>>>>

@@

\begin{table}[ht]
    \centering
    \caption{Mean, median and standard deviation of trait affinities that were responsive to the salinity gradient in the original study but not when re-analysis with the harmonized dataset trait dataset.} 
    \label{tab:SI_resp_traits_summary_stats}
    \begin{tabular}{llccc}
    \toprule[.1em]
    Dataset & Trait & Mean & Median & SD \\ 
    \toprule[.1em]
    Stepw\_median & Shredder & 0.20 & 0.14 & 0.25 \\ 
      Stepw\_mean & Shredder & 0.18 & 0.12 & 0.22 \\ 
      Direct\_median & Shredder & 0.21 & 0.14 & 0.25 \\ 
      Direct\_mean & Shredder & 0.19 & 0.14 & 0.22 \\ 
      Weighted & Shredder & 0.19 & 0.14 & 0.22 \\ 
      Harmonized; not\_aggregated & Shredder & 0.18 & 0.12 & 0.24 \\ 
      Original & Shredder & 0.25 & 0.14 & 0.32 \\ 
      Stepw\_median & Gills & 0.30 & 0.27 & 0.32 \\ 
      Stepw\_mean & Gills & 0.29 & 0.22 & 0.32 \\ 
      Direct\_median & Gills & 0.30 & 0.30 & 0.32 \\ 
      Direct\_mean & Gills & 0.30 & 0.30 & 0.32 \\ 
      Weighted & Gills & 0.30 & 0.30 & 0.32 \\ 
      Harmonized; not\_aggregated & Gills & 0.30 & 0.25 & 0.32 \\ 
      Original & Gills & 0.28 & 0.00 & 0.33 \\ 
      Stepw\_median & Short life cycle & 0.64 & 0.75 & 0.39 \\ 
      Stepw\_mean & Short life cycle & 0.64 & 0.79 & 0.39 \\ 
      Direct\_median & Short life cycle & 0.67 & 0.75 & 0.37 \\ 
      Direct\_mean & Short life cycle & 0.67 & 0.79 & 0.38 \\ 
      Weighted & Short life cycle & 0.67 & 0.79 & 0.38 \\ 
      Harmonized; not\_aggregated & Short life cycle & 0.64 & 0.75 & 0.40 \\ 
      Original & Short life cycle & 0.64 & 0.75 & 0.40 \\ 
      Stepw\_median & Long life cylce & 0.36 & 0.25 & 0.39 \\ 
      Stepw\_mean & Long life cylce & 0.36 & 0.21 & 0.39 \\ 
      Direct\_median & Long life cylce & 0.33 & 0.25 & 0.37 \\ 
      Direct\_mean & Long life cylce & 0.33 & 0.21 & 0.38 \\ 
      Weighted & Long life cylce & 0.33 & 0.21 & 0.38 \\ 
      Harmonized; not\_aggregated & Long life cylce & 0.36 & 0.25 & 0.40 \\ 
      Original & Long life cylce & 0.36 & 0.25 & 0.40 \\ 
    \bottomrule
    \end{tabular}
\end{table}
